An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-03-05 Paper.tex
Minor edits
Edit mathematical appendix
This commit tightens up the mathematical reasoning and corrects some errors
and omissions.

@@

\citet{ClW:06,ClW:07} base their \oos\ statistic on the right side
of~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
the size of the test sample used to evaluate the forecasting models.
\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
use a rolling window of length $R$ (i.e., $\hat{y}_{t+1}$ is a
function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
$z_{t-R}$ where $z_t$ is another weakly dependent random process),
which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
the weak dependence properties of the variables used to estimate it.
Keeping $R$ finite ensures that the conditional variance remains
positive, so the sum obeys a \clt.  This method of ensuring normality
was introduced by \citet{GiW:06}.  The coefficients $\beta_0$ are
assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
the null hypothesis) and Clark and West propose using this statistic
to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
$\mathcal{F}_t$.  In \citet{ClW:07}, $\beta_0$ is unknown but is
estimated with a fixed-length rolling window as well, so
\begin{equation*}
  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=t-R+1}^t x_{t-1} y_t
\end{equation*}
and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
$\varepsilon_{t+1}$ in the test statistic for \mds.  Unfortunately,
$\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
$\varepsilon_{t+1}$ is, so the statistic is no longer asymptotically
mean-zero normal, even though this approximation performs well in the
simulations reported by \citet{ClW:07}.

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
    $\bar f(\beta_0)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \osum{t} g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

\begin{thm}\label{res:2}
  Suppose the conditions of Lemma~\ref{res:1} hold, with assumptions
  on the alternative model, $\hat{y}_{1t}$, holding for each of the
  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$ and let the subscript
  $l$ denote the different quantities associated with $\hat{y}_{lt}$
  (i.e. $\mathcal{F}_{lt}$, etc.)  Also assume that the long-run
  variance-covariance matrix of the vector
  $(\bar{f}_1(\beta_0),\dots,\bar{f}_m(\beta_0))'$ is uniformly
  positive definite.

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} \bar{f}_{i} > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-\alpha$ quantile of $\max_{i \notin M_{j-1}}
    \tfrac{1}{\hat{\sigma}_i^{*}}(\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1}))$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length $1$, has probability at most $\alpha$ of
    rejecting one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
    f_i(\beta_0) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
    \infty$ (for the stationary bootstrap) or $b \to \infty$ and
    $\frac{b}{P} \to 0$ (for the moving or circular block bootstraps)
    then the procedure outlined above controls \sfwe\ at level
    $\alpha$ for the family of null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \sfwe\ at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_0) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\beta_0) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    and $\E h_{s}(\beta_0) = 0$ for all $s$.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and twice continuously
    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
    uniformly bounded ($r$ is defined below), and there exists a
    sequence of random variables $m_t$ such that $\sup_{i,\beta \in N}
    |\tfrac{\partial^2}{\partial \beta \partial \beta'}
    \psi_{it}(\beta)| \leq m_t$ almost surely and $\E m_t^2$ is
    uniformly finite.
  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
      uniform mixing processes, $r = 2$ is also allowed as long as
      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
      integrable.}
  \item The sequence $\psi_1^{*},\dots,\psi_T^{*}$ is generated by the
    moving blocks, circular blocks, or stationary bootstrap with block
    lengths drawn from the geometric distribution.  The (expected)
    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T h_t^* = 0$ a.s.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{rem}
  \citet{CoS:07} use the distribution of $\sqrt{P}(\bar{f}^{*} -
  \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\hat{\beta}_T)$
  is the bootstrap analogue of $\E \bar{f}(\beta_0)$, the parameter of
  interest.  Because their bootstrap is miscentered, \citet{CoS:07}
  must redefine $\hat{\beta}_t^{*}$ to achieve consistency.  In this
  paper, though, consistency arises naturally.
\end{rem}

@@

\newcommand{\WesA}{\oclt{t} (\nabla
  f_t^*(\hat\beta_{T}) - F^*) B^* H_t^*}
\newcommand{\WesB}{\tfrac{1}{\sqrt{P}} F^* \osum{t} (B_t^* -
  B^*) H_t^*}
\newcommand{\WesC}{\oclt{t} (\nabla
  f_t^*(\hat\beta_{T}) - F^*) (B_t^* - B^*) H_t^*}
\begin{proof}[Proof of Theorem~\ref{res:3}]
  Expand $\E^{*} f_t^{*}(\hat{\beta}_t^{*})$ around $\hat{\beta}_{T}$
  to get
  \begin{align*}
    \sqrt{P} (\bar{f}^{*} - \bar{f}(\hat{\beta}_{T})) &= \oclt{t}
    f_t^{*}(\hat{\beta}_{T}) - \bar{f}(\hat{\beta}_{T}) +
    F^{*} B^{*} \oclt{t} H_t^* \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t^*
  \end{align*}
  where (as in \citealp{Wes:96}) the $i$th element of $w_t^*$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_T)'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
    f_{it}^*(\tilde\beta_{it}^*) \Big]
    (\hat\beta_t^* - \hat\beta_T)
  \end{equation*}
  and each $\tilde\beta_{it}^*$ lies between $\hat\beta_t^*$ and
  $\hat\beta_T$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
  identical to West's, using our Lemma~\ref{res:a2} in place of his
  Lemma A3.  Then
  \begin{gather}
    \WesA \to^{p^*} 0 \label{eq:7} \\
    \WesB \to^{p^*} 0 \label{eq:9} \\
  \intertext{and}
    \WesC \to^{p^*} 0 \label{eq:10}
  \end{gather}
  from Lemma~\ref{res:a4} and the result follows from Lemma~\ref{res:a3}.
\end{proof}

@@

\section{Supporting Results}
This Appendix restates \citepos{Mcc:00} results, which themselves
weaken \citepos{Wes:96} assumptions, but under the dependence
conditions of Theorem~\ref{res:1}.  It also proves Lemmas required for
that result and the results in the main paper.

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
    \to^{p^{*}} 0$.
  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_T |
    \to^{p^{*}} 0$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}] \quad
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}$ satisfies \citepos[Theorem
    3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s} \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s} \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.  \citepos{Cal:11d} Theorem~2 ensures the same argument
    holds for $\tfrac{1}{\sqrt{T}} h_s^{*}$.
  \item We have
    \begin{multline}
      P^a \sup_t | \hat{\beta}_t - \beta_0 | = P^a \sup_t |\hat{B}_{t}
      H_{t}| \\ \leq \sup_{t,u \in S_T} \Big| [ \hat{B}_u - B]
      \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big| + \sup_{t\in S_T} \Big|
      B \tfrac{P^a}{t} \sum_{s=1}^t h_{s} \Big|
    \end{multline}
    and both terms converge to zero in (conditional) probability by
    the previous argument and by assumption.  The same argument holds
    for $\hat{\beta}_t^{*} - \hat{\beta}_{T+1}$ as well.
  \end{enumerate}
\end{proof}

>>>>

\newcommand{\btrue}[1][]{\if#1*\hat\beta_{T+1}\else\beta_0\fi}

@@

\citet{ClW:06,ClW:07} base their \oos\ statistic on the right side
of~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
the size of the test sample used to evaluate the forecasting models.
\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
use a rolling window of length $R$ (i.e., $\hat{y}_{t+1}$ is a
function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
$z_{t-R}$ where $z_t$ is another weakly dependent random process),
which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
the weak dependence properties of the variables used to estimate it.
Keeping $R$ finite ensures that the conditional variance remains
positive, so the sum obeys a \clt.  This method of ensuring normality
was introduced by \citet{GiW:06}.  The coefficients $\beta_0$ are
assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
the null hypothesis) and Clark and West propose using this statistic
to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
$\mathcal{F}_t$.  In \citet{ClW:07}, $\beta_0$ is unknown but is
estimated with a fixed-length rolling window as well, so
\begin{equation*}
  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{s-1} x_{s-1}'\Big)^{-1}
  \sum_{s=t-R+1}^t x_{s-1} y_s
\end{equation*}
and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
$\varepsilon_{t+1}$ in the test statistic for \mds.  Unfortunately,
$\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
$\varepsilon_{t+1}$ is, so the statistic is no longer asymptotically
mean-zero normal, even though this approximation performs well in the
simulations reported by \citet{ClW:07}.

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$, $\hat{y}_{1t}$, and $x_t$
    have uniformly bounded $2 r$ moments for some $r > 2$, and $\hat
    y_t y_t$ $\hat y_t x_{t-1}$, $y_t x_{t-1}$, and $x_{t-1},
    x_{t-1}'$ are $L_2$-\ned\ of size $-\frac12$ on a strong mixing
    series of size $-\frac{r}{r-2}$ for $r>2$ or a uniform mixing
    series of size $-\frac{r}{2r-2}$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \oavg{t} f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
    $\bar f(\beta_0)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \oavg{t} (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \oavg{t} (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \oavg{t} (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \osum{t} g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

\begin{thm}\label{res:2}
  Suppose the conditions of Theorem~\ref{res:1} hold, with assumptions
  on the alternative model, $\hat{y}_{1t}$, holding for each of the
  $m$ models $\hat{y}_{1t}, \dots, \hat{y}_{mt}$ and let the subscript
  $l$ denote the different quantities associated with $\hat{y}_{lt}$
  (i.e. $\mathcal{F}_{lt}$, etc.)  Also assume that the long-run
  variance-covariance matrix of the vector
  $(\bar{f}_1(\beta_0),\dots,\bar{f}_m(\beta_0))'$ is uniformly
  positive definite.

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} \bar{f}_{i} > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-\alpha$ quantile of $\max_{i \notin M_{j-1}}
    \tfrac{1}{\hat{\sigma}_i^{*}}(\bar{f}_{i}^{*} -
    \bar{f_i}(\btrue[*]))$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length $1$, has probability at most $\alpha$ of
    rejecting one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
    f_i(\beta_0) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
    \infty$ (for the stationary bootstrap) or $b \to \infty$ and
    $\frac{b}{P} \to 0$ (for the moving or circular block bootstraps)
    then the procedure outlined above controls \sfwe\ at level
    $\alpha$ for the family of null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \sfwe\ at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k \times q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$; $H_{t}$ is a sequence of $q$-vectors such that
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}(\beta_0) & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}(\beta_0) & \text{fixed window} \\
      \end{cases}
    \end{equation}
    and $\E h_{s}(\beta_0) = 0$ for all $s$.
  \item Define $\psi_t(\beta) = (f_t(\beta), h_t(\beta))$;
    $\psi_t(\beta)$ is covariance stationary and twice continuously
    differentiable in an open neighborhood $N$ of $\beta_0$.  Also,
    $\E \sup_{\beta \in N} |\psi_t(\beta)|^r$ and $\E\sup_{\beta \in
      N} |\frac{\partial}{\partial \beta} \psi_t(\beta)|^r$ are
    uniformly bounded, and there exists a sequence of random variables
    $m_t$ such that $\sup_{i,\beta \in N} |\tfrac{\partial^2}{\partial
      \beta \partial \beta'} \psi_{it}(\beta)| \leq m_t$ almost surely
    and $\E m_t^2$ is uniformly finite.
  \item Both $\psi_t(\beta)$ and $\frac{\partial}{\partial \beta}
    \psi_t(\beta)$ are $L_2$-\ned\ of size $-\frac12$ on the
    series $V_t$ with bounded \ned-coefficients for $\beta$ uniformly
    in $N$; $V_t$ is strong mixing of size $-\frac{r}{r-2}$ or uniform
    mixing of size $-\frac{r}{2r-2}$ with $r > 2$.\footnote{For
      uniform mixing processes, $r = 2$ is also allowed as long as
      $\sup_{\beta \in N} \psi_t(\beta)^2$ and $\sup_{\beta \in N}
      (\partial \psi_t(\beta) / \partial \beta)^2$ are uniformly
      integrable.}
  \item The sequence $\psi_1^{*},\dots,\psi_T^{*}$ is generated by the
    moving blocks, circular blocks, or stationary bootstrap with block
    lengths drawn from the geometric distribution.  The (expected)
    block length $b$ satisfies $b \to \infty$ and $\frac{b}{P} \to 0$.
  \item The bootstrapped estimator satisfies $\sup_t |\hat{B}_t^{*} -
    B^{*}| \to^p 0$, $B^{*} = B + o_p$ and $\frac1T \sum_{t=1}^T h_t^* = 0$ a.s.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite.
  \item $R, P \to \infty$ as $T \to \infty$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\btrue[*]))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{rem}
  \citet{CoS:07} use the distribution of $\sqrt{P}(\bar{f}^{*} -
  \bar{f})$ to approximate that of $\sqrt{P}(\bar{f} - \E
  \bar{f}(\beta_0))$.  But it is clear that $\bar{f}(\btrue[*])$
  is the bootstrap analogue of $\E \bar{f}(\beta_0)$, the parameter of
  interest.  Because their bootstrap is miscentered, \citet{CoS:07}
  must redefine $\hat{\beta}_t^{*}$ to achieve consistency.  In this
  paper, though, consistency arises naturally.
\end{rem}

@@

\newcommand{\WesA}[1][]{\oclt{t} (\nabla
  f_t^{#1}(\btrue[#1]) - F^{#1}) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\tfrac{1}{\sqrt{P}} F^{#1} \osum{t} (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\oclt{t} (\nabla
  f_t^{#1}(\btrue[#1]) - F^{#1}) (B_t^{#1} - B^{#1}) H_t^{#1}}
\begin{proof}[Proof of Theorem~\ref{res:3}]
  Expand $f_t^{*}(\hat{\beta}_t^{*})$ around $\btrue[*]$
  to get
  \begin{align*}
    \sqrt{P} \big(\bar{f}^{*} - \bar{f}(\btrue[*])\big) &= \oclt{t}
    \big(f_t^{*}(\btrue[*]) - \bar{f}(\btrue[*])\big) +
    F^{*} B^{*} \oclt{t} H_t^* \\
    & \quad + \WesA[*] + \WesB[*] \\ & \quad + \WesC[*] + \oclt{t} w_t^*
  \end{align*}
  where (as in \citealp{Wes:96}) the $i$th element of $w_t^*$ is
  \begin{equation*}
    w_{it} = \tfrac12 (\hat\beta_t^* - \hat\beta_{T+1})'
    \Big[\tfrac{\partial^2}{\partial \beta \partial\beta'} 
    f_{it}^*(\tilde\beta_{it}^*) \Big]
    (\hat\beta_t^* - \hat\beta_{T+1})
  \end{equation*}
  and each $\tilde\beta_{it}^*$ lies between $\hat\beta_t^*$ and
  $\hat\beta_{T+1}$.  The argument that $\oclt{t} w_t^* = o_{p^*}(1)$ is
  identical to West's, using our Lemma~\ref{res:a2} in place of his
  Lemma A3.  Then
  \begin{gather}
    \WesA[*] \to^{p^*} 0 \label{eq:7} \\
    \WesB[*] \to^{p^*} 0 \label{eq:9} \\
  \intertext{and}
    \WesC[*] \to^{p^*} 0 \label{eq:10}
  \end{gather}
  from Lemma~\ref{res:a4} and the result follows from
  Lemma~\ref{res:a3}, with the form of the asymptotic variance
  following directly from \citet{Wes:96} and \citet{WeM:98}.
\end{proof}

@@

\section{Supporting Results}

\begin{lema}\label{res:a2}
  Suppose $a \in [0,\frac12)$ and the conditions of Theorem~\ref{res:3}
  hold.
  \begin{enumerate}
  \item $P^a \sup_t | H_{t} | \to^p 0$ and $P^a \sup_t | H_{t}^{*} |
    \to^{p^{*}} 0$.
  \item $P^a \sup_t | \hat{\beta}_{t} - \beta_{0} | \to^{p} 0$ and
    $P^a \sup_t | \hat{\beta}^{*}_{t} - \hat{\beta}_T |
    \to^{p^{*}} 0$.
  \item $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
    \big(\tfrac{\partial}{\partial \beta} f_t(\beta_0) - F\big) =
    O_{p}(1)$ and $\tfrac{1}{\sqrt{P}} \sum_{t=R+1}^T
    \big(\tfrac{\partial}{\partial \beta} f_t^*(\hat\beta_{T+1}) -
    F^*\big) = O_{p^*}(1)$.
  \end{enumerate}
\end{lema}

\begin{proof}[Proof of Lemma~\ref{res:a2}]
  \begin{enumerate}
  \item The process $\tfrac{1}{\sqrt{T}} h_{s}(\beta_0)$ satisfies
    \citepos[Theorem 3.1]{JoD:00b} functional \clt.  So
    \begin{equation}
      P^a \sup_t \Big| \tfrac1t \sum_{s=1}^t h_{s}(\beta_0) \Big| =
      P^a \sup_{\gamma \in [0,1]} \Big| \tfrac{1}{\lfloor \gamma
        T\rfloor} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}(\beta_0) \Big| \to^{p} 0
    \end{equation}
    with the convergence following from the continuous mapping
    theorem.  For the bootstrapped average, \citepos{Cal:11d}
    Theorem~2 ensures that
    \begin{equation}
      \tfrac{1}{\sqrt{\gamma
          T}} \sum_{s=1}^{\lfloor \gamma T \rfloor} h_{s}^*(\hat\beta_{T+1}) 
      = O_{p^*}(\Omega^*(\hat\beta_{T+1})^{1/2})
    \end{equation}
    where $\Omega^*(\beta) = \var^* h_t^*(\beta)$.  Since
    $\hat\beta_{T+1} \to^p \beta_0$, it suffices to show that
    $\sup_{\beta \in N} | \Omega^*(\beta) - \var h_t(\beta) | \to^p
    0$.  But this convergence holds for any fixed $\beta$ and our
    assumptions guarantee stochastic equicontinuity as in
    \citet{JoD:00} \citep[also see][]{Dav:94}, completing the proof.
